### 2021-03-02 paper.Rmd
spinifex section init and bib.

- tourr (Di) and spinifex (Nick)
- liminal (Stuart)

>>>>

- tourr (Di) 
- spinifex (Nick)

The R package spinifex [@spyrison_spinifex_2020] has 3 primary features: it produces manual tours (predefined path or interactive manipulation, identifies orthonormal global feature bases with the use of the Rdimtools [@you_rdimtools_2020] package, renders (manual or other) tours as animations exportable to static .gif or interactive .html widgets, lastly it offers interactive shiny application that offers an graphical user interface to quickly sample tour features.

- liminal (Stuart)
